\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{helvet}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\renewcommand{\familydefault}{\sfdefault}

% Define section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}


\vspace{0.5cm}

\section*{Ahmed Klabi}
Tunis, Tunisia | +216 26709297 | ahmetklabi10@gmail.com | github.com/ahmedkltn | linkedin.com/in/ahmedkltn

\section*{Summary}
Highly analytical Data Engineer & Analyst with proven experience in real-time ETL pipeline development, KPI analytics, and ML model deployment.  Proficient in Python, SQL, and Golang, with expertise in GCP and BigQuery.  Passionate about building scalable, reliable data systems and delivering actionable insights to drive business results.  Seeking to leverage expertise in data warehousing and cloud technologies to contribute to Free2move's innovative mobility solutions.

\section*{Experience}
\subsection*{The Quantic Factory — Data Scientist}
Jan 2024 – Present | Tunis, Tunisia

\begin{itemize}
    \item Engineered and maintained real-time ETL pipelines using Golang, processing marketing data into BigQuery and GCS, ensuring data accuracy and reliability.
    \item Developed and implemented GeoLift A/B testing using SeekTable, resulting in a 15\% increase in ROAS and revenue.
    \item Designed and developed software tools for business users to compute custom eCommerce KPIs, enhancing customer and product insights.
    \item Developed advanced SQL queries to transform raw marketing and product data into actionable insights, powering dashboards and weekly business reports utilized by key stakeholders.
    \item Automated reporting workflows using Claude LLM in Python, streamlining business decision-making processes.
    \item Deployed Isolation Forest-based anomaly detection models to proactively mitigate data quality issues.
\end{itemize}

\subsection*{Algorithmics Global — Coding Instructor}
Aug 2023 – Present | Remote

\begin{itemize}
    \item Instructed 150+ students (ages 7–15) in Python fundamentals and algorithmic thinking using Jupyter Notebooks, fostering logical and creative problem-solving skills.
    \item Guided students through the development of beginner Python projects (games, automation tools), building foundational programming skills.
\end{itemize}

\subsection*{Media Center Development — Data Analyst Intern}
Aug 2022 – Sep 2022 | Sfax, Tunisia

\begin{itemize}
    \item Web scraped 91,000+ pricing records using BeautifulSoup & Scrapy for comprehensive eCommerce market analysis.
    \item Performed in-depth analysis of pricing trends and anomalies to support data-driven pricing optimization strategies.
\end{itemize}

\section*{Projects}
\begin{itemize}
    \item \textbf{Auto Pricing Scraper:} Scraped 10K+ car listings; performed data cleaning and developed predictive models using pandas & scikit-learn.
    \item \textbf{Glassdoor Analyzer:} Scraped job/salary data using Scrapy; visualized tech hiring trends using matplotlib.
    \item \textbf{Reddit Sentiment App:} Developed a real-time sentiment tracker using PRAW, TextBlob, and Streamlit.
\end{itemize}

\section*{Technical Skills}
\textbf{Data Engineering \& Cloud:} BigQuery, GCS, Pub/Sub, Cloud Run, MySQL, ClickHouse, Docker, Git, AWS (S3 - from project experience)
\textbf{ML \& NLP:} scikit-learn, TensorFlow, Keras, TextBlob, Isolation Forest, Claude LLM
\textbf{Languages:} Python, SQL, Golang, R
\textbf{Tools \& APIs:} Jupyter, SeekTable, BeautifulSoup, Scrapy, Streamlit, REST APIs


\section*{Education}
\subsection*{TEK-UP University}
CS Engineering (Part-Time) | Sep 2024 – Present

\subsection*{ISIM Mahdia}
BSc in Business Computing, Minor: Business Intelligence | Sep 2021 – Jun 2024


\end{document}